---
title: "Homework 2"
author: "Duubar Villalobos Jimenez"
date: "February 10, 2018"
output:
  pdf_document: default
  html_document: default
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


#install.packages("install.load")
library(install.load)
install_load("plyr", "dplyr", "pracma", "mat2tex")

```

# 1. Problem set 1


## (1)
**Show that $AA^T \neq A^TA$ in general. (Proof and demonstration.)**

### Answer

+ Proof

In order to proof, I will focus by checking the sizes of the matrices involved.

First, lets define our $A$ matrix with a size $m \times n$.

Where $1 \leq n, 1 \leq m$.

By definition, its transpose $A^T$ has size $n \times  m$.

a) By definition (matrix multiplication), we have that $AA^T$ has size $m \times n$ times $n \times m$ resulting in a matrix of size $m \times m$

b) By definition (matrix multiplication), we have that $A^TA$ has size $n \times m$ times $m \times n$ resulting in a matrix of size $n \times n$

Then, by comparing we conclude that the matrices have different sizes since $m$ is not necessarily the same as $n$.

+ Conclusion

$AA^T \neq A^TA$

+ Demonstration


$$A=\begin{pmatrix}1&4&-3\\ \:6&3&0\end{pmatrix}$$

```{r vector_definitions, echo=TRUE}
A <- matrix(c(1,4,-3,
              6,3,0), ncol=3, byrow=TRUE)
```

Let's see  $A^T$.

```{r, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE, results='asis'}
xx("A^T =", t(A), digits=0)
```

Solving $AA^T$

```{r, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE, results='asis'}
aat <- xx("AA^T =", A %*% t(A), digits=0) 
aat
```

Solving $A^TA$

```{r, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE, results='asis'}
ata <- xx("A^TA =", t(A) %*% A, digits=0) 
ata
```



## (2)
**For a special type of square matrix $A$, we get $A^TA = AA^T$ . Under what conditions could this be true? (Hint: The Identity matrix I is an example of such a matrix)**

### Answer

This condition could be true if $A$ is a Symmetric Matrix; that is $A = A^T$; and by $A$ being a symmetric matrix, then A is square $m \times m$ matrix.


# 2. Problem set 2

Write an R function to factorize a square matrix $A$ into LU or LDU, whichever you prefer.

```{r}
# Based matrix as example 3x3
A1 <- matrix(c(1,4,-3,
              6,3,0,
              2,4,3), ncol=3, byrow=TRUE)

# Based matrix as example 4x4
A <- matrix(c(1,-2,-2,-3,
              3,-9,0,-9,
              -1,2,4,7,
              -3,-6,26,2), ncol=4, byrow=TRUE)
```

*Building L*

```{r}
# Function that creates the Identity matrix in order to create our L matrix from it
build_L <- function(A){
  
  L <- matrix(,nrow = dim(A)[1], ncol = dim(A)[1])
  
  for (i in 1:dim(A)[1]){
       for (j in 1:dim(A)[1]){
            L[i,j]<- 0 # Assign 0     
       }
      L[i,i]<- 1 # Assign 1 
  }
  return(L)
}
```

*Finding LU*

```{r}
# Function that finds and return the LU matrices.
find_LU <- function(U){
  
  L <- build_L(U) # Building L Matrix

  # Procedure to find Upper and Lower Matrix
  for (i in 1:dim(U)[1] ){
       k <- i + 1
       if (k <= dim(U)[1]) {
         for (j in k:dim(U)[1]){

            L[j,i] <- (U[j,i] / U[i,i]) 
            U[j,] <- -1 * (U[j,i] / U[i,i]) * U[i,] + U[j,]
  
            #print(U)
            #print(L)
         }
       }
  }
  LU <- list(U, L)
  return(LU)
}
```

```{r}
LU <- find_LU(A)
U <- matrix(unlist(LU[1]), ncol=dim(A)[1], nrow=dim(A)[1])
L <- matrix(unlist(LU[2]), ncol=dim(A)[1], nrow=dim(A)[1])
```

### Original Matrix

```{r, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE, results='asis'}
A <- xx("A =", A, digits=0) 
A
```


### Lower Matrix

```{r, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE, results='asis'}
L <- xx("L =", L, digits=0) 
L
```

### Upper Matrix

```{r, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE, results='asis'}
U <- xx("U =", U, digits=0) 
U
```
