---
title: "Homework 1"
author: "Duubar Villalobos Jimenez"
date: "January 30, 2018"
output:
  pdf_document: default
  html_document: default
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("pracma")
library(pracma)
```

# 1. Problem set 1


## (1)
**Calculate the dot product u.v where u = [0.5; 0.5] and v = [3; -4]**

### Answer

+ Defining vectors

```{r vector_definitions, echo=TRUE}
u <- c(0.5, 0.5)
v <- c(3, -4)
```

+ Defining function

```{r dot_funtion_definition, echo=TRUE}
dot_product <- function(u,v){
  product <- dot(u,v)
  return(product)
}
```

+ Answer

The dot product u.v = `r dot_product(u,v)`.

+ By hand

```{r dot_funtion1_definition, echo=TRUE}
d <- (0.5 * 3) + (0.5 * (-4))
```

+ Answer

The dot product u.v = `r d`.

## (2)
**What are the lengths of u and v? Please note that the mathematical notion of the length of a vector is not the same as a computer science definition.**

### Answer

+ In Computer Science:

```{r cs_len_vectors, echo=TRUE}
cs_vect_len <- function(v){
  len <- length(v)
  return(len)
} 
```

The length of $u$ is `r cs_vect_len(u)`.

The length of $v$ is `r cs_vect_len(v)`.

+ In Mathematics

```{r math_len_vectors, echo=TRUE}
math_vect_len <- function(v){
  cum_sum <- 0
  for (value in v){
    cum_sum <- cum_sum + value * value
  }
  mth_vect_len <- sqrt(cum_sum)
  return(mth_vect_len)
}

# Google search
goog_vect_len <- function(x) sqrt(sum(x^2))
```

The length of $u$ is `r math_vect_len(u)`.

The length of $v$ is `r goog_vect_len(v)`.

## (3)
**What is the linear combination: $3u - 2v$?**

### Answer

```{r linear_comb, echo=TRUE}
w <- 3*u - 2*v
```

The linear combination is the vector w = [`r w`].

## (4) 
**What is the angle between $u$ and $v$**

### Answer

Since the dot product of two vectors $x$ and $y$ is defined as follows:

$$x . y = ||x|| . ||y|| cos(\theta)$$


```{r angle, echo=TRUE}
len_u <- goog_vect_len(u)
len_v <- goog_vect_len(v)
dot_uv <- dot_product(u,v)
theta_angle_uv <- acos(dot_uv / (len_u * len_v))
```

The angle in between the vectors $u$ and $v$ is `r theta_angle_uv`.

# 2. Problem set 2

## Defining variables

```{r SLE_01, echo=TRUE}
x <- c('x1', 'x2', 'x3')
```

## Defining Matrix

```{r SLE_02, echo=TRUE}
A <- matrix(data = c( 1,  1, 3,
                      2, -1, 5,
                     -1, -2, 4)
            , nrow=3, byrow = TRUE)
```

## Defining vector

```{r SLE_03, echo=TRUE}
b <- c(1, 2, 6)
```

## Writing Function

```{r SLE_04, echo=TRUE}

GJEP <- function(A, x, b){
  
  # Augmenting the matrix A
  A <- cbind(A,b)
  
  # Renaming columns for matrix A
  colnames(A) <- c("[,1]","[,2]","[,3]","[,4]")
  
  # Focus on Row 1
  if ((A[1,1] == 0) && (A[2,1] != 0)) {
    temp <- A[1,]
    A[1,] <- A[2,]
    A[2,] <- temp
  }
  
  if (A[1,1] != 1) {
    A[1,] <- A[1,] / A[1,1]
  }

  # Focus on Row 2 and 3
  if (A[2,1] != 0) {
    scalar = -1 * A[2,1]
    A[2,] <- scalar *  A[1,] +  A[2,]
  }
  
  if (A[3,1] != 0) {
    scalar = -1 * A[3,1]
    A[3,] <- scalar *  A[1,] +  A[3,]
  }
  
  # Focus on Row 2
  if ((A[2,2] == 0) && (A[3,2] != 0)) {
    temp <- A[2,]
    A[2,] <- A[3,]
    A[3,] <- temp
  }

  if (A[2,2] != 1) {
    A[2,] <- A[2,] / A[2,2]
  }

  # Focus on Row 3
  if (A[3,2] != 0) {
  scalar = -1 * A[3,2]
  A[3,] <- scalar *  A[2,] +  A[3,]
  }

  
  if (A[3,3] != 0)  {
    if (A[3,3] != 1) {
      A[3,] <- A[3,] / A[3,3]
    }
  }
  
  # Finding Solutions
  x3 <- A[3,4]
  x2 <- A[2,4] - A[2,3] * x3
  x1 <- A[1,4] - A[1,3] * x3 - A[1,2] * x2
  
  xx <- c(x1, x2, x3)
  
  xx <- round(xx,2)
  
  return(xx)
}

```

###  Solution

```{r}
sol <- GJEP(A,x,b)
```

The solution for the system will be S = {(`r x[1]` = `r sol[1]`, `r x[2]` = `r sol[2]`, `r x[3]` = `r sol[3]`)}













