---
title: "Homework 3"
author: "Duubar Villalobos Jimenez"
date: "February 17, 2018"
output:
  pdf_document: default
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
  html_document: default
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# https://github.com/friendly/matlib
#library(devtools)
#install_github("friendly/matlib", build_vignettes = TRUE)

#install.packages("install.load")
library(install.load)
install_load("pracma", "mat2tex", "matrixcalc", "matlib") 
```

# 1. Problem set 1


## (1)
**What is the rank of the matrix A?**

$$A= \begin{pmatrix}1&2&3&4\\ -1&0&1&3\\ 0&1&-2&1\\ 5&4&-2&-3\end{pmatrix}$$

### Answer


```{r }
A <- matrix(data = c(1,2,3,4,
                     -1,0,1,3,
                     0,1,-2,1,
                     5,4,-2,-3), ncol=4, byrow=TRUE)
```

Let's see the Echelon form with steps (thanks to *echelon* function from the *matlib* library).

```{r}

#https://github.com/friendly/matlib
echelon(A, verbose = TRUE, fractions = TRUE)

```


Based on the definition of Rank of a Matrix: _Suppose that $A$ is an $m \times n$ matrix. Then the rank of $A$ is the dimension of the column space of $A, r (A) = dim (C(A))$._ 


```{r}

r <- matrix.rank(A)

```

Now, since we have four rows with values equal to 1 in different columns, then the rank will be r(A) = `r r`.



## (2)

**Given an $m \times n$ matrix where $m > n$, what can be the maximum rank? The minimum rank, assuming that the matrix is non-zero?**

### Answer

In order to respond to this, we can do as follows:

Since we have $m > n$, we can easily say that $m$ could be equal to $m=n+1$ *OR* $m=n+2$, *OR* ... $m=n+k$.

From the above, we can deduct that $k=m-n$. 

For simplicity reasons, we can say that we can represent our matrix as follows:

$$A_{m \times n} = A_{(n+k) \times n}$$
**What can be the maximum rank?**

Now, since we have more rows than columns the maximum number of columns that could be reduced in the Echelon form will be $n$ columns. Hense the maximum rank of the matrix will be $r(Matrix)=n$.

**What can be the minimum rank?**

I would say that the minimum rank of such matrix will be $1$, since that's the minimum number of inputs in any given row in order to have a non zero matrix.



## (3)
**What is the rank of matrix B?**

$$B=\begin{pmatrix}1&2&1\\ 3&6&3\\ 2&4&2\end{pmatrix}$$

### Answer

```{r}
B <- matrix(data = c(1,2,1,
                     3,6,3,
                     2,4,2), ncol=3, byrow=TRUE)
```


Let's see the Echelon form with steps (thanks to *echelon* function from the *matlib* library).

```{r}
echelon(B, verbose = TRUE, fractions = TRUE)
```


```{r}

r <- matrix.rank(B)

```

Now, since we have one row with values equal to 1 in the first column, then the rank will be r(A) = `r r`.


# 1. Problem set 2

**Compute the eigenvalues and eigenvectors of the matrix $A$. You’ll need to show your work. You’ll need to write out the characteristic polynomial and show your solution.**

$$A=\begin{pmatrix}1&2&3\\ 0&4&5\\ 0&0&6\end{pmatrix}$$

## Answer

Let's define our matrix A and I.

```{r}
A <- matrix(data = c(1,2,3,
                     0,4,5,
                     0,0,6), ncol=3, byrow=TRUE)

I <- matrix(data = c(1,0,0,
                     0,1,0,
                     0,0,1), ncol=3, byrow=TRUE)
```

$$f_A (\lambda) =\det \left(\begin{pmatrix}1&2&3\\ \:0&4&5\\ \:0&0&6\end{pmatrix}-\lambda \begin{pmatrix}1&0&0\\ \:0&1&0\\ \:0&0&1\end{pmatrix}\right)$$

$$f_A (\lambda) =\det \begin{pmatrix}1-\lambda&2&3\\ 0&4-\lambda&5\\ 0&0&6-\lambda\end{pmatrix}=\left(-\lambda+1\right)\left(-\lambda+4\right)\left(-\lambda+6\right)$$

$$f_A (\lambda) = -\lambda^3+11\lambda^2-34\lambda+24$$

From the above procedure, our characteristic polynomial will be:

```{r}
charpoly(A, info = FALSE)
```

$$f_A (\lambda) = \lambda^3-11\lambda^2+34\lambda-24$$

When comparing the hand solution versus the charpoly solution, we notice that each value has same numerical results but with oposite signs. This should not be a problem once we solve for the equation $f_A (\lambda) = 0$


From the above, we can conclude that our eigenvalues are as follows:

$$\left(-\lambda+1\right)\left(-\lambda+4\right)\left(-\lambda+6\right)=0$$

$\lambda_1=1$,  $\lambda_2=4$,   $\lambda_3=6$

**R Solution**

```{r}
E <- eigen(A, symmetric=FALSE)
E$values
```

And by solving each equation $(A-\lambda I_3)x=0$ we can obtain our eigenvectors.

For $\lambda_1=1$

$$\left(\begin{pmatrix}1&2&3\\ 0&4&5\\ 0&0&6\end{pmatrix}-(1)\cdot\begin{pmatrix}1&0&0\\ 0&1&0\\ 0&0&1\end{pmatrix}\right)\begin{pmatrix}x_1\\ x_2\\ x_3\end{pmatrix}=\begin{pmatrix}0\\ 0\\ 0\end{pmatrix}$$

$$\begin{pmatrix}0&2&3\\ 0&3&5\\ 0&0&5\end{pmatrix}\begin{pmatrix}x_1\\ x_2\\ x_3\end{pmatrix}=\begin{pmatrix}0\\ 0\\ 0\end{pmatrix}$$

$$=\begin{pmatrix}0x_1 + 2x_2+3x_3\\ 0x_1+3x_2+5x_3\\ 0x_1+0x_2+5x_3\end{pmatrix}=\begin{pmatrix}0\\ 0\\ 0\end{pmatrix}$$

From the above equation, we can conclude that $x_1$ can take any value, but for simplicity reasons, we will assign $x_1=1$.

For $\lambda_1=1$ the Eigenvector will be:

$x_3 =0$, $x_2=0$, $x_1=1$

$$E_f(\lambda=1)=\begin{pmatrix}1\\ 0\\ 0\end{pmatrix}$$


Similar steps need to be performed for $\lambda_2=4$ and $\lambda_3=6$ in order to obtain our final result as follows:

$\lambda_2=4$

$$\left(\begin{pmatrix}1&2&3\\ 0&4&5\\ 0&0&6\end{pmatrix}-(4)\cdot\begin{pmatrix}1&0&0\\ 0&1&0\\ 0&0&1\end{pmatrix}\right)\begin{pmatrix}x_1\\ x_2\\ x_3\end{pmatrix}=\begin{pmatrix}0\\ 0\\ 0\end{pmatrix}$$

$$E_f(\lambda=4)=\begin{pmatrix}2\\ 3\\ 0\end{pmatrix}$$

$\lambda_2=6$

$$\left(\begin{pmatrix}1&2&3\\ 0&4&5\\ 0&0&6\end{pmatrix}-(6)\cdot\begin{pmatrix}1&0&0\\ 0&1&0\\ 0&0&1\end{pmatrix}\right)\begin{pmatrix}x_1\\ x_2\\ x_3\end{pmatrix}=\begin{pmatrix}0\\ 0\\ 0\end{pmatrix}$$

$$E_f(\lambda=6)=\begin{pmatrix}16\\ 25\\ 10\end{pmatrix}$$

**R Solution**

After comparing our solutions, I have noticed that the results differ a lot! I have done some research and found out that the Eigenvectors calculated in R uses the LAPACK routines (http://www.netlib.org/). 

LAPACK is a library of Fortran 77 subroutines for solving the most commonly occurring problems in numerical linear algebra. It has been designed to be efficient on a wide range of modern high-performance computers. The name LAPACK is an acronym for Linear Algebra PACKage. 


```{r}
E$vectors
```


In this case R returns the following eigenvectors wich are efficient numerical approximations to our previous hand results.

$E_f(\lambda=6)=$ [`r E$vectors[,1]`]

$E_f(\lambda=4)=$ [`r E$vectors[,2]`]

$E_f(\lambda=1)=$ [`r E$vectors[,3]`]
