---
title: "Discussion 2"
author: "Duubar Villalobos Jimenez"
date: "February 5, 2018"
output:
  pdf_document: default
  html_document: default
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# C27 † Page 353

**Book:** Beezer: A First Course in Linear Algebra

## Exercise

Doing the computations by hand, find the determinant of the matrix A.

$$A = \begin{pmatrix}1\:&\:0\:&\:1\:&\:1\:\\ \:2\:&\:2\:&\:-1\:&\:1\:\\ \:2\:&\:1\:&\:3\:&\:0\:\\ \:1\:&\:1\:&\:0\:&\:1\end{pmatrix}$$

### Solution

First, I will reduce the matrix as follows:

Swap matrix rows: $R_1\:\leftrightarrow R_2$

$$=\begin{pmatrix}2&2&-1&1\\ 1&0&1&1\\ 2&1&3&0\\ 1&1&0&1\end{pmatrix}$$

Cancel leading coefficient in row $R_2$ by performing $R_2\:\leftarrow \:R_2-\frac{1}{2}\cdot \:R_1$

$$=\begin{pmatrix}2&2&-1&1\\ 0&-1&\frac{3}{2}&\frac{1}{2}\\ 2&1&3&0\\ 1&1&0&1\end{pmatrix}$$

Cancel leading coefficient in row  $R_3$ by performing $R_3\:\leftarrow \:R_3-1\cdot \:R_1$

$$=\begin{pmatrix}2&2&-1&1\\ 0&-1&\frac{3}{2}&\frac{1}{2}\\ 0&-1&4&-1\\ 1&1&0&1\end{pmatrix}$$

Cancel leading coefficient in row  $R_4$ by performing $R_4\:\leftarrow \:R_4-\frac{1}{2}\cdot \:R_1$

$$=\begin{pmatrix}2&2&-1&1\\ 0&-1&\frac{3}{2}&\frac{1}{2}\\ 0&-1&4&-1\\ 0&0&\frac{1}{2}&\frac{1}{2}\end{pmatrix}$$

Cancel leading coefficient in row  $R_3$ by performing $R_3\:\leftarrow \:R_3-1\cdot \:R_2$

$$=\begin{pmatrix}2&2&-1&1\\ 0&-1&\frac{3}{2}&\frac{1}{2}\\ 0&0&\frac{5}{2}&-\frac{3}{2}\\ 0&0&\frac{1}{2}&\frac{1}{2}\end{pmatrix}$$

Cancel leading coefficient in row  $R_4$ by performing $R_4\:\leftarrow \:R_4-\frac{1}{5}\cdot \:R_3$

$$=\begin{pmatrix}2&2&-1&1\\ 0&-1&\frac{3}{2}&\frac{1}{2}\\ 0&0&\frac{5}{2}&-\frac{3}{2}\\ 0&0&0&\frac{4}{5}\end{pmatrix}$$

Since the determinant of the matrix equals the diagonal product of the matrix:

$$det(A)=2\left(-1\right)\frac{5}{2}\cdot \frac{4}{5}$$

$$det(A)=-4$$

Now, since I have interchanged two rows, it negate the determinant, therefore multiply the result by $\left(-1\right)^1$.

$$det(A)=\left(-1\right)^1\left(-4\right)=4$$

## Solving in R

+ Defining Matrix

```{r det, }
A <- matrix(data = c(1,0,1,1,
                     2,2,-1,1,
                     2,1,3,0,
                     1,1,0,1), ncol=4, byrow=TRUE)
```

+ Finding determinant in R

```{r det1, }
det(A)
```



