---
title: "Discussion 9"
author: "Duubar Villalobos Jimenez   mydvtech@gmail.com"
date: "March 28, 2018"
output:
  pdf_document: default
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
    prettydoc:code_folding: hide
  html_document: default
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1)
```


```{r library_setup, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(xtable)
library(plyr)
type='html'
```


# 1 † Page 338

**Book:** Grinstead: Introduction to Probability

## Exercise

Let $S_{100}$ be the number of heads that turn up in 100 tosses of a fair coin. Use the Central Limit Theorem to estimate the below exercises:


### Preamble

The second fundamental theorem of probability is the **Central Limit Theorem**. This theorem says that if $S_n$ is the sum of n mutually independent random variables, then the distribution function of $S_n$ is well-approximated by a certain type of continuous function known as a **normal density function**, which is given by the formula

$$f_{\mu, \sigma}(x) = \frac{e^{-\frac{(x - \mu)^2}{2 \sigma^2}}}{\sigma \sqrt{2 \pi }} $$
Also, from the above information provided, we know as follows:

$n = 100$

$p = 0.5$

$\mu = np$

$\mu = 100 \times 0.5 = 50$

$\sigma^2 = np(1-p)$

$\sigma^2 = 100 \times 0.5 \times (1 - 0.5)$

$\sigma = \sqrt{100 \times 0.5 \times (1 - 0.5)}$

$\sigma = 5$

Also, The Central Limit for Bernoulli Trials says as follows:

Let $S_n$ be the number of successes in $n$ Bernoulli trials with probability $p$ for success, and let $a$ and $b$ be two fixed real numbers. Then

$$lim_{n \to \infty} P \left( a \le S_n \le b \right) = \int_a^b{f_{\mu, \sigma}(x)dx}$$

For demonstration purposes, I will write a small function that find it's approximation based on the Central Limit Theorem using the **normal density function** only.


```{r, echo=TRUE}
# This can also be calculated by using >>>>>   pnorm(b, mu, sigma)   <<<<<
CLT <- function(a, b){
  mu <- 50
  sigma <- 5
  ndf <- function(x){exp(1)^(-(x - 50)^2 / (2 * 5^2)) / (5 * sqrt(2 * pi))}
  p_ndf <- integrate(ndf, lower = a, upper = b)
  return(p_ndf$value)
}
```


```{r, echo=FALSE}
plot.density <- function(a,b){
  mean <- 50 # mu
  sd <- 5    # sigma
  x<-seq(0,100,0.01)
  y<-dnorm(x,mean,sd) 
  plot(x,y,type="l") 
  polygon(c( x[x<=b], b ),  c(y[x<=b],0 ), col="red")
  polygon(c( x[x<=a], a ),  c(y[x<=a],0 ), col="white")
  title("Normal Density Function")
}
```

### (a) P ($S_{100} \le 45$).

```{r, echo=FALSE}
plot.density(0,45)
```

The probability will be `r round(CLT(0,45),4)` or `r round(CLT(0,45) * 100,2)`%.


### (b) P ($45 < S_{100} < 55$).

```{r, echo=FALSE}
plot.density(45,55)
```

The probability will be `r round(CLT(45,55),4)` or `r round(CLT(45,55) * 100,2)`%.


### (c) P ($S_{100} > 63$).


```{r, echo=FALSE}
plot.density(63,100)
```

The probability will be `r round(CLT(63,100),4)` or `r round(CLT(63,100) * 100,2)`%.



### (d) P ($S_{100} < 57$).


```{r, echo=FALSE}
plot.density(0,57)
```

The probability will be `r round(CLT(0,57),4)` or `r round(CLT(0,57) * 100,2)`%.
