---
title: "Discussion 5"
author: "Duubar Villalobos Jimenez"
date: "February 28, 2018"
output:
  pdf_document: default
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
  html_document: default
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#.libPaths()
#.libPaths( c( .libPaths(), "/home/mydvadmin/anaconda3/lib/R/library") )

#install.packages("install.load")
library(install.load)
install_load("pracma", "prettydoc")
```

# 5 † Page 13

**Book:** Grinstead: Introduction to Probability

## Exercise

Consider the bet that all three dice will turn up sixes at least once in n rolls of three dice. Calculate $f(n)$, the probability of at least one triple-six when three dice are rolled n times. Determine the smallest value of n necessary for a favorable bet that a triple-six will occur when three dice are rolled n times. 

(DeMoivre would say it should be about $216 \cdot log(2) = 149.7$ and so would answer 150—see Exercise 1.2.17. Do you agree with him?)

### Solution

For this, we could approach it in two different forms.

+ The probability of wining by having one six in one dice is as follows:

For this, let's say $X$ will be the action of rolling the dice.

Probability of Wining = $P(X = 6) = \frac{1}{6}$  

OR  

Probability of Wining = 1 - Probability of loosing.

Probability of Wining = $1 - P(X \neq 6) = 1-\frac{5}{6}$

From here, we can deduct as follows:

+ The probability of wining by having three sixes in one roll is as follows:

$P(X_1 = 6) = \frac{1}{6}$ and

$P(X_2 = 6) = \frac{1}{6}$ and 

$P(X_3 = 6) = \frac{1}{6}$

This means as follows:

$P(X_1 = 6 \cap X_2 = 6 \cap X_2 = 6) = \frac{1}{6} \cdot \frac{1}{6} \cdot \frac{1}{6} = \frac{1}{6^3}$

OR

$1-P(X_1 \neq 6) = 1-\frac{5}{6}$ and 

$1-P(X_2 \neq 6) = 1-\frac{5}{6}$ and

$1-P(X_3 \neq 6) = 1-\frac{5}{6}$

From here we can also deduct that the probability of winning can be as follows:

Probability of wining = $\left ( 1-P(X_1 \neq 6) \right ) \cdot \left ( 1-P(X_2 \neq 6) \right ) \cdot \left ( 1-P(X_3 \neq 6) \right )$

Probability of wining = $\left ( 1-\frac{5}{6} \right ) \cdot \left ( 1-\frac{5}{6} \right ) \cdot \left (1-\frac{5}{6} \right )$

Probability of wining =  $\left ( 1-\frac{5}{6} \right )^3$

Probability of wining =  $\left ( \frac{6}{6}-\frac{5}{6} \right )^3$

Probability of wining =  $\left ( \frac{1}{6} \right )^3$

Probability of wining =  $\frac{1}{6^3}$

By creating a table of rolls, we can deduct as follows:

```{r, echo=FALSE}
n <- 6
n_roll <- c()
pX1 <- c()
pX2 <- c()
pX3 <- c()
pXWin3_6 <- c()
pCumXWin3_6 <- c()


 for (i in 1:n){
   n_roll[i] <- i
   pX1[i] <- "1/6"
   pX2[i] <- "1/6"
   pX3[i] <- "1/6"
   pXWin3_6[i] <- "1/6^3"
   pCumXWin3_6[i] <- paste(i, "/6^3")
 }

   n_roll[n+1] <- "..."
   pX1[n+1] <- "1/6"
   pX2[n+1] <- "1/6"
   pX3[n+1] <- "1/6"
   pXWin3_6[n+1] <-  "1/6^3"
   pCumXWin3_6[n+1] <- paste("...")
   
   n <- n+1
   n_roll[n+1] <- "n"
   pX1[n+1] <- "1/6"
   pX2[n+1] <- "1/6"
   pX3[n+1] <- "1/6"
   pXWin3_6[n+1] <-  "1/6^3"
   pCumXWin3_6[n+1] <- paste("n/6^3")

pTable <- data.frame(n_roll, pX1, pX2, pX3, pXWin3_6, pCumXWin3_6)

pTable
```

Based on the above table our probability of winning function will be as follows:

$$f(n) = \frac{n}{6^3}$$

And we want to know for which n, $f(n) > \frac{1}{2}$?

for this, we solve the inequation as follows:

$$ \frac{n}{6^3} > \frac{1}{2}$$

$$ n > \frac{6^3}{2}$$

$n > 108$

Based on that; the smallest value of $n$ necessary for a favorable bet that a triple-six will occur when three dice are rolled $n$ times will be $109$ times.

**Programing in R**

```{r}
f <- function(n){
  f <- n / (6 ^ 3)
  return(f)
}
```

Let's generate a table of probabilities

```{r}
p <- function(n){
  n_roll <- c()
  fn <- c()
  for (i in 1:n) {
    n_roll[i] <- i
    fn[i] <- f(i)
  }
  fn <- data.frame(n_roll, fn)
  return(fn)
}
```

Let's see our table for $n = 109$

```{r}
n <- 109
pn <- p(n)
pn[n,]
```

Table of probabilities:

```{r}
pn
```

### Just for fun

Let's generate random picks for 3 dice 100000 times and see if at least one of those rolls get three sixes on the same "roll" before the 109 roll.

```{r}
n <- 109 # Minimum n required to get 3 sixes on the same roll

roll_3_dice <- function(n){  
  n_roll <- c()
  X1 <- c()
  X2 <- c()
  X3 <- c()
  pXWin3_6 <- c()
  Win <- c()
  for (i in 1:n){
     n_roll[i] <- i
     X1[i] <- as.numeric(round(runif(1, 1, 6),0))
     X2[i] <- as.numeric(round(runif(1, 1, 6),0))
     X3[i] <- as.numeric(round(runif(1, 1, 6),0))
     pXWin3_6[i] <- as.numeric(X1[i]) + as.numeric(X2[i]) + as.numeric(X3[i]) # Maximum addition will be 18; this will mean triple 6 came up
     if (pXWin3_6[i] == as.numeric(18)) {
        Win[i] <- "YES"
     }
     else {
       Win[i] <- "NO"
     }
  }
  pTable <- data.frame(n_roll, X1, X2, X3, pXWin3_6, Win)
  return(pTable)
}
```

**Rolling 3 dice 100000 times.**

```{r}
results <- roll_3_dice(100000)
subset(results, Win == "YES")
```

Let me know what you think.
