---
title: "Discussion 8"
author: "Duubar Villalobos Jimenez   mydvtech@gmail.com"
date: "March 21, 2018"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
    prettydoc:code_folding: hide
  pdf_document: default
  html_document: default
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1)
```


```{r library_setup, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(xtable)
library(plyr)
type='html'
```


# 5 † Page 289

**Book:** Grinstead: Introduction to Probability

## Exercise

Consider the following two experiments: the first has outcome X taking on the values 0, 1, and 2 with equal probabilities; the second results in an (in-dependent) outcome Y taking on the value 3 with probability 1/4 and 4 with probability 3/4. Find the distribution of:

### Solution

```{r, echo=FALSE}
X <- c( 0,   1,   2  )
px <- c(1/3, 1/3, 1/3)
x_table <- data.frame('Outcome' = X, 'Probability' = as.character(px))
```

```{r, echo=FALSE, results='asis'}
print(xtable(x_table, caption='Probability Table for Outcome X.', digits=0),hline.after=c(0,3), include.rownames=FALSE, type=type, comment=FALSE)
```



```{r, echo=FALSE}
Y <- c( 3, 4)
py <- c(1/4, 3/4)
y_table <- data.frame('Outcome' = Y, 'Probability' = as.character(py))
```

```{r, echo=FALSE, results='asis'}
print(xtable(y_table, caption='Probability Table for Outcome Y.', digits=0),hline.after=c(0,2), include.rownames=FALSE, type=type, comment=FALSE)
```


### a) Y + X.


```{r, echo=FALSE}
i <- 1
Sn <- c()
Sk <- c()
SnP <- c()
SnPk <- c()
for ( x in X){
  for ( y in Y){
    Sk[i] <- paste0(as.character(y), ' + ', as.character(x))
    Sn[i] <- y + x
    i <- i + 1
  }
}
i <- 1
for ( x in px){
  for ( y in py){
    SnPk[i] <- paste0(as.character(y), ' x ', as.character(x))
    SnP[i] <- y * x
    i <- i + 1
  }
}

S_table <- data.frame('Operation'=Sk, 'Result' = as.character(Sn), 'Convoluted' = SnPk, 'Probability' =  SnP)
```

```{r, echo=FALSE, results='asis'}
print(xtable(S_table, caption='Probability Table of individual Outcomes Sn = Y + X.', digits=4),hline.after=c(0,6), include.rownames=FALSE, type=type, comment=FALSE)
```

```{r,echo=FALSE}
SnU <- unique(Sn)
```

From the above table, we can deduct that our possible outcomes for Sn are as follows: Sn = {`r SnU`}.

From here we can deduct our probabilities as follows:

```{r, echo=FALSE}
i <- 1
p <- c()
for (n in Sn){
  p[i] <- sum(S_table$Probability[S_table$Result == n])
  i <- i + 1
}

S_table <- data.frame('Sn' = as.character(Sn), 'Probability' = p, 'Percentage' = paste(round(p*100,2),'%'))

S_table <- S_table[!duplicated(S_table), ] # dropping duplicate rows
```

```{r, echo=FALSE, results='asis'}
print(xtable(S_table, caption='Probability Table for Unique Outcomes Sn = Y + X.', digits=4),hline.after=c(0,4), include.rownames=FALSE, type=type, comment=FALSE)
```


### b) Y - X.



```{r, echo=FALSE}
i <- 1
Sn <- c()
Sk <- c()
SnP <- c()
SnPk <- c()
for ( x in X){
  for ( y in Y){
    Sk[i] <- paste0(as.character(y), ' - ', as.character(x))
    Sn[i] <- y - x
    i <- i + 1
  }
}
i <- 1
for ( x in px){
  for ( y in py){
    SnPk[i] <- paste0(as.character(y), ' x ', as.character(x))
    SnP[i] <- y * x
    i <- i + 1
  }
}

S_table <- data.frame('Operation'=Sk, 'Result' = as.character(Sn), 'Convoluted' = SnPk, 'Probability' =  SnP)
```

```{r, echo=FALSE, results='asis'}
print(xtable(S_table, caption='Probability Table of individual Outcomes Sn = Y - X.', digits=4),hline.after=c(0,6), include.rownames=FALSE, type=type, comment=FALSE)
```

```{r,echo=FALSE}
SnU <- sort(unique(Sn))
```

From the above table, we can deduct that our possible outcomes for Sn are as follows: Sn = {`r SnU`}.

From here we can deduct our probabilities as follows:

```{r, echo=FALSE}
i <- 1
p <- c()
for (n in Sn){
  p[i] <- sum(S_table$Probability[S_table$Result == n])
  i <- i + 1
}

S_table <- data.frame('Sn' = as.character(Sn), 'Probability' = p, 'Percentage' = paste(round(p*100,2),'%'))

S_table <- S_table[!duplicated(S_table), ] # dropping duplicate rows

S_table <- arrange(S_table,Sn)
```

```{r, echo=FALSE, results='asis'}
print(xtable(S_table, caption='Probability Table for Unique Outcomes Sn = Y - X.', digits=4),hline.after=c(0,4), include.rownames=FALSE, type=type, comment=FALSE)
```









Let me know what you think.



