---
title: "Discussion 1"
author: "Duubar Villalobos Jimenez"
date: "February 1, 2018"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
  pdf_document: default
  html_document: default
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# C17 † Page 42

## Exercise

Find all solutions to the system of linear equations. Use your favorite computing device to row-reduce the augmented matrices for the systems, and write the solutions as a set, using correct set notation.

$−x_1 + 5x_2 = −8$

$−2x_1 + 5x_2 + 5x_3 + 2x_4 = 9$

$−3x_1 − x_2 + 3x_3 + x_4 = 3$

$7x_1 + 6x_2 + 5x_3 + x_4 = 30$

### Preparation

In oder to solve this linear system, we need to set up our square matrix by taking the left side values from the equal sign and I will call it $C$; our right side values of the equal sign will be represented in a vector, I will call it $d$.

```{r matrix-setup, include=TRUE, echo=TRUE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

C = matrix(data = c(-1,-2,-3,7,5,5,-1,6,0,5,3,5,0,2,1,1), nrow=4, ncol = 4)
d = c(-8,9,3,30)

```

Matrix $C$.

```{r C_matrix, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

C

```

Vector $d$.

```{r d_vector, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

d

```

### Solving in R using 'solve'

We can solve this equation by using the following command.

```{r matrix_solve, include=TRUE, echo=TRUE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

solve(C,d)

```

#### Answer

$$ S = \{(x_1 = 3, x_2 = -1, x_3 = 2, x_4 = 5)\}$$

### Solving in R using 'Row Reduction' (Gauss-Jordan Elimination)

For this, we need to use the package 'pracma'.

```{r pracma, include=TRUE, echo=TRUE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

#install.packages("pracma")
library("pracma")

```

Setup into a single matrix, I will call it $G$.

```{r pracma_setup, include=TRUE, echo=TRUE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

G = matrix(data = c(-1,-2,-3,7,5,5,-1,6,0,5,3,5,0,2,1,1,-8,9,3,30), nrow=4, ncol = 5)

```

Representation of matrix $G$.

```{r G_Matrix, include=TRUE, echo=FALSE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

G

```


We can solve this equation by using the following command.

```{r pracma_solve, include=TRUE, echo=TRUE, warning=FALSE, error=FALSE, cache=FALSE, message=FALSE}

rref(G)

```

#### Answer

$$ S = \{(x_1 = 3, x_2 = -1, x_3 = 2, x_4 = 5)\}$$

