---
title: "Discussion 3"
author: "Duubar Villalobos Jimenez"
date: "February 11, 2018"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
  pdf_document: default
  html_document: default
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("install.load")
library(install.load)
install_load("pracma")
```

# C12 † Page 388

**Book:** Beezer: A First Course in Linear Algebra

## Exercise

Find the characteristic polynomial of the matrix A.

$$A = \begin{pmatrix}1&2&1&0\\  1&0&1&0\\  2&1&1&0\\  3&1&0&1\end{pmatrix}$$

### Solution

A characteristic polynomial of square matrix $A$ is defined as $f_A (\lambda) = \det \left(A-\lambda I\right)$ where $I$ is the identity matrix of same dimension as $A$.

$$f_A (\lambda) =  \det \left(A-\lambda I\right)$$

First, I will calculate $\left(A-\lambda I\right)$

$$\begin{pmatrix}1&2&1&0\\ 1&0&1&0\\ 2&1&1&0\\ 3&1&0&1\end{pmatrix}- \lambda\begin{pmatrix}1&0&0&0\\ 0&1&0&0\\ 0&0&1&0\\ 0&0&0&1\end{pmatrix}=\begin{pmatrix}1- \lambda&2&1&0\\ 1&- \lambda&1&0\\ 2&1&1- \lambda&0\\ 3&1&0&1- \lambda\end{pmatrix}$$

Now, I will proceed to find determinant $\left(A-\lambda I\right)$.

$$\det \left(A-\lambda I\right) = \det \begin{pmatrix}1- \lambda&2&1&0\\ 1&- \lambda&1&0\\ 2&1&1- \lambda&0\\ 3&1&0&1- \lambda\end{pmatrix}$$

By reducing the matrix to row echelon form, have :

$$\det \left(A-\lambda I\right) = \det \begin{pmatrix}1- \lambda&2&1&0\\ 0&\frac{- \lambda-5}{- \lambda+1}&-\frac{3}{- \lambda+1}&- \lambda+1\\ 0&0&\frac{2\left(2 \lambda+3\right)}{ \lambda+5}&-\frac{- \lambda^3+2 \lambda^2+ \lambda-2}{- \lambda-5}\\ 0&0&0&-\frac{ \lambda^4-3 \lambda^3-2 \lambda^2+2 \lambda+2}{2\left(2 \lambda+3\right)}\end{pmatrix}$$

Since the determinant of the matrix equals the diagonal product of the matrix.

$$\det \left(A-\lambda I\right) = \left(1- \lambda\right)\frac{- \lambda-5}{- \lambda+1}\cdot \frac{2\left(2 \lambda+3\right)}{ \lambda+5}\left(-\frac{ \lambda^4-3 \lambda^3-2 \lambda^2+2 \lambda+2}{2\left(2 \lambda+3\right)}\right)$$

By simpliying the above expression, we obtain as follows:

$$\det \left(A-\lambda I\right) = \lambda^4-3\lambda^3-2\lambda^2+2\lambda+2$$

Since $f_A (\lambda) =  \det \left(A-\lambda I\right)$


The answer will be:

$$f_A (\lambda) = \lambda^4-3\lambda^3-2\lambda^2+2\lambda+2$$


## Solving in R

+ Defining Matrix

```{r det, }
# https://www.rdocumentation.org/packages/pracma/versions/1.9.9/topics/charpoly

A <- matrix(data = c(1,2,1,0,
                     1,0,1,0,
                     2,1,1,0,
                     3,1,0,1), ncol=4, byrow=TRUE)
```

+ For this I will employ the charpoly function from the pracma library in R.

```{r charpoly }
charpoly(A, info = FALSE)
```

To interpret the answer, it will be as follows:

$$f_A (\lambda) = \lambda^4-3\lambda^3-2\lambda^2+2\lambda+2$$



