---
title: "Discussion 6"
author: "Duubar Villalobos Jimenez"
date: "March 7, 2018"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: leonids
    toc: yes
    prettydoc:code_folding: hide
  pdf_document: default
  html_document: default
subtitle: CUNY MSDS DATA 605
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1)
```

# Libraries

In this section, I will include all libraries needed.

```{r libraries,}
libraries <- c(
              "plotly",
              "tidyverse",
              "xtable"
              )
```

```{r library_setup, include=FALSE}
library(install.load)
install_load(libraries)
```

# 9 † Page 89

**Book:** Grinstead: Introduction to Probability

## Exercise

A more refined inequality for approximating $n!$ is given by

$$\sqrt{2\pi n} \left( \frac{n}{e} \right)^n e^{1/(12n+1)} < n! < \sqrt{2\pi n} \left( \frac{n}{e} \right)^n e^{1/(12n)}$$
Write a computer program to illustrate this inequality for n = 1 to 9.

## Solution

+ Left Side

```{r}
factorial_left <- function(n){
  n_row <- c()
  fact_l <- c()
  fact_l[1] <- 1
  e <- exp(1)
  for (i in 1:n){
    n_row[i] <- i
    fact_l[i] <- round(sqrt(2 * pi * i) * (i / e)^(i) * e^( 1 / (12 * i + 1) ),2)
  }
  fact_l <- data.frame('n' = n_row, 'n_left' =fact_l)
  return(fact_l)
}

```

+ Factorial

```{r}
factorial_center <- function(n){
  n_row <- c()
  fact_c <- c()
  nfac <- 1
  e <- exp(1)
  for (i in 1:n){
    nfac <- nfac * i
    n_row[i] <- i
    fact_c[i] <- nfac
  }
  fact_c <- data.frame('n' = n_row, 'n_center' =fact_c)
  return(fact_c)
}

```

+ Right Side

```{r}
factorial_right <- function(n){
  n_row <- c()
  fact_r <- c()
  fact_r[1] <- 1
  e <- exp(1)
  for (i in 1:n){
    n_row[i] <- i
    fact_r[i] <- round(sqrt(2 * pi * i) * (i / e)^(i) * e^( 1 / (12 * i ) ),2)
  }
  fact_r <- data.frame('n' = n_row, 'n_right' =fact_r)
  return(fact_r)
}

```


## Table

Even though is not very clear in the plot, by looking at the results, we can notice that yes, in fact these approximations illustrate the inequality!


```{r, echo=FALSE}
n <- 9
fl <- factorial_left(n)
fc <- factorial_center(n)
fr <- factorial_right(n)
compare_factorial <- data.frame(fl$n, fl$n_left, fc$n_center, fr$n_right)
names(compare_factorial)[1] <- "n"
names(compare_factorial)[2] <- "left side"
names(compare_factorial)[3] <- "n!"
names(compare_factorial)[4] <- "right side"
```



```{r, echo=FALSE, warning=FALSE, results='asis'}
print(xtable(compare_factorial, caption='n! Comparison Table.', digits=2),hline.after=c(0,9), include.rownames=FALSE, type='html', comment=FALSE, floating = getOption("xtable.floating", FALSE))
```

## Plot

```{r, echo=FALSE}
p <- plot_ly(compare_factorial, x = ~`n`, y = ~`right side`, type = 'scatter', mode = 'lines+markers', name = 'Top') %>%
             add_trace(y = ~`n!`, mode = 'lines+markers', name =  "n!") %>%
             add_trace(y = ~`left side`, mode = 'lines+markers', name =  "Bottom") %>%
             layout(title = 'n! Comparison', #" Single Mortality Rates by State and Year",
                    xaxis = list(categoryorder = "array",
                                 categoryarray = ~`n`,
                                 type = "category"),
                    yaxis = list(title = "n!"))
```



```{r, echo=FALSE}
p
```






